Reliable error estimation for Sobol' indices\thanks{This work is supported by the CITiES project funded by the Agence Nationale de la Recherche (grant ANR-12-MONU-0020) and by the United States National Science Foundation (grant DMS-1522687).}

### 2017-05-16 article_review2.0/Manuscript.tex
new repo for revision

\begin{abstract}
In the field of sensitivity analysis, Sobol' indices are sensitivity measures widely used to assess the importance of inputs of a model to its output. The estimation of these indices is often performed {\color{purple}through} Monte Carlo or quasi-Monte Carlo methods. A notable method is the replication procedure that estimates first-order indices at a reduced cost in terms of number of model evaluations.

@@

A practical problem concerning the use of these methods is how to quantify the number of model evaluations required to ensure that Sobol' estimates are accurate enough. This article addresses this challenge by proposing a reliable error bound for Sobol' indices based on digital sequences. \comment{One reason to use digital sequences is that the numerical integration convergence rates are of $\mathcal{O}(n^{-1+\delta})$ ($n$ being the number of function values) instead of the usual $\mathcal{O}(n^{-1/2})$ for iid Monte Carlo methods. In addition,} the error bound in this article is defined in terms of the discrete Walsh coefficients of the integrands involved in the Sobol' indices definition. We propose a sequential estimation procedure of Sobol' indices using the error bound as our stopping criterion. The procedure operates under the assumption that all integrands lie inside a particular cone of functions (see \cite{HicJim}).

@@

\subsection{Definition of Sobol' indices}
\label{sec:2.1}
%We adopt the same notations introduced by Owen in \cite{Owen}. 
Denote by $\vx=(x_1,\dots,x_d)$ the vector of inputs of $f$. We assume that $f$ is in some subset of $\in \mathbb{L}^2(\cube)$ for which $f(\vx)$ is defined for all $\vx\in\cube$, and $\mathcal{D}=\{1,\dots,d\}$ the set of dimension indexes. %The uncertainty on $\vx$ is modeled by a random vector that we suppose uniformly distributed on $\cube$.
Let $u$ be a subset of $\mathcal{D}$, $-u$ its complement and $|u|$ its cardinality. Then, $\vx_u$ represents a point in $[0,1]^{|u|}$ with components $x_j, j \in u$. Given two points $\vx$ and $\vx'$, the hybrid point $\vw=(\vx_u:{\vx'}_{-u})$ is defined as $w_j=x_j$ if $j \in u$ and $w_j=x'_j$ if $j \notin u$.% and denote by $\mu$ and $\sigma^2$ the mean $\int_{\cube}f(\vx)d{\vx}$ and variance $\int_{\cube}(f(\vx)-\mu)^2d{\vx}$ of $f$.

@@

\subsection{Estimation of Sobol' indices}
\label{sec:2.2}
In this section we review two Monte Carlo procedures for the estimation of Sobol' indices. A design is a point set $\mathcal{P}=\{\vx_i\}_{i=0}^{n-1}$ where each point is obtained by sampling each variable $x_j$ $n$ times. Each row of the design is a point $\vx_i$ in $[0,1]^d$ and each column of the design refers to samples of a variable $x_j$. Consider $\mathcal{P}=\{\vx_i\}_{i=0}^{n-1}$ and $\mathcal{P'}=\{{\vx'}_i\}_{i=0}^{n-1}$ two designs where $(\vx_i,{\vx'}_i) \iid \mathcal{U}([0,1]^{2d})$. One way to estimate the two quantities (\ref{first.order}) and (\ref{total.effect}) is via:
\begin{align}
\label{first.order.est}
\widehat{\underline{\tau}_u^2} &= \frac{1}{n} \sum \limits_{i=0}^{n-1} \left(f(\vx_{i,u}:{\vx'}_{i,-u})-f(\vx'_i)\right)f(\vx_i),\\
\label{total.effect.est}
\widehat{\ov{$\tau$}_u^2} &= \frac{1}{2n} \sum \limits_{i=0}^{n-1} (f({\vx'}_i) - f(\vx_{i,u}:{\vx'}_{i,-u}))^2, \qquad u \in \mathcal{D},
\end{align}
using for $\sigma^2$:
{\color{purple} 
\begin{equation}
 \widehat{\sigma}^2 = \frac{1}{n-1} \sum \limits_{i=0}^{n-1} \left( f(\vx_i) - \widehat{\mu}\right)^2, \text{ with } \ \widehat{\mu} =  \frac{1}{n} \sum \limits_{i=0}^{n-1} f(\vx_i).
\label{mu.est}
\end{equation}
}
Then, the Sobol' indices estimators are:
\begin{equation}
\widehat{\underline{S}}_u = \widehat{\underline{\tau}_u^2} / \widehat{\sigma}^2, \qquad
\widehat{\overline{S}}_u = \widehat{\overline{\tau}_u^2} / \widehat{\sigma}^2.
\label{common.sobol.est}
\end{equation}
Using this method, the estimation of a single pair ($\widehat{\underline{S}}_u$, $\widehat{\overline{S}}_u$) requires $3n$ evaluations of the model $f$. Thus, for all first order and total effect indices, one would need $3nd$ model evaluations. Using a combinatorial formalism, in \cite{Saltelli} Saltelli proposes the following estimation strategy:
\begin{theorem}
\label{saltelli.theorem}
The $d+2$ designs $\{\vx_{i,u}:{\vx'}_{i,-u}\}_{i=0}^{n-1}$ constructed for $u \in \{\varnothing,\{1\},\dots,$ $\{d\},\mathcal{D}\}$ allow to estimate all first-order and total effect Sobol' indices at a cost of $n(d+2)$ evaluations of the model.
\end{theorem}
The main idea of the theorem is that there is no need to reevaluate $f({\vx}_i)$ and $f({\vx'}_i)$ for each $u$. Hence, we can simply evaluate $f({\vx}_i)$ $n$ times, $f({\vx'}_i)$ $n$ times, and $f(\vx_{i,u}:{\vx'}_{i,-u})$ $nd$ times, which accounts for the $n(d+2)$ evaluations.

The $d+2$ designs of Theorem \ref{saltelli.theorem} are obtained by substituting columns of $\mathcal{P}$ for columns of $\mathcal{P}'$ {\color{purple}according} to $u$. While elegant, this approach requires a number of model evaluations that grows linearly with respect to the input \break space dimension.

A more efficient alternative to evaluate all first-order indices was proposed in \cite{Mara} and only requires $2n$ model evaluations. This alternative relies on the construction of two replicated designs. The notion of replicated designs was first introduced by McKay through his replicated Latin Hypercubes in \cite{McKay}. In order to apply this definition to other types of points, in \cite{GJAHMP} we generalized this notion to the following.

{\color{purple}  
\begin{definition}
\label{rep.designs}
Let $\mathcal{P}=\{\vx_i\}_{i=0}^{n-1}$ and $\mathcal{P}'=\{{\vx'}_i\}_{i=0}^{n-1}$ be two point sets in $[0,1]^{d}$. In these sets, all points $\vx_i$ (resp. $\vx'_i$) are coordinate-wise different, i.e. for all $(i_1,i_2) \in \{0,\dots,n-1\}^2$ such that $i_1 \neq i_2$: $$x_{i_1,j} \neq x_{i_2,j}, \qquad \text{for any  } j=1,\dots,d .$$
Let $\mathcal{P}^u=\{\vx_{i,u}\}_{i=0}^{n-1}$ (resp. ${\mathcal{P}'}^u$), $u \subsetneq \mathcal{D}$, denote the subset of dimensions of $\mathcal{P}$ (resp. $\mathcal{P}'$) indexed by $u$. We say that $\mathcal{P}$ and $\mathcal{P}'$ are two replicated designs of order $a \in \{1,\dots,d-1\}$ if for any $u \subsetneq \mathcal{D}$ such that $|u|=a$, $\mathcal{P}^u$ and ${\mathcal{P}'}^u$ are the same point set in $[0,1]^a$. We define by $\pi_u$ the permutation that rearranges the rows of ${\mathcal{P}'}^u$ into $\mathcal{P}^u$ and exclude the trivial case $\vx_i = \vx'_i$ for all $i\in\{0,\dots,n-1\}$.
\end{definition}
}

@@

More precisely, let $\mathcal{P}=\{\vx_i\}_{i=0}^{n-1}$ and $\mathcal{P}'=\{{\vx'}_i\}_{i=0}^{n-1}$ be two replicated designs of order $1$. Denote by $\{y_i\}_{i=0}^{n-1}=$\\$\{f(\vx_i)\}_{i=0}^{n-1}$ and $\{y'_i\}_{i=0}^{n-1}=\{f({\vx'}_i)\}_{i=0}^{n-1}$ the two sets of model evaluations obtained with $\mathcal{P}$ and $\mathcal{P}'$. From Definition \ref{rep.designs}, we know that ${\vx'}_{\pi_u(i),u}={\vx}_{i,u}$. Then,
\begin{align*}
y'_{\pi_u(i)}&= f(\vx'_{\pi_u(i),u}:{\vx'}_{\pi_u(i),-u}) \\
&= f(\vx_{i,u}:{\vx'}_{\pi_u(i),-u}).
\end{align*}
Hence, each $\underline{\tau}^2_u$ can be estimated via formula (\ref{first.order.est}) by using $y'_{\pi_u(i)}$ instead of $f(\vx_{i,u}:{\vx'}_{i,-u})$ without requiring further model evaluations for each $u$. This estimation method has been studied deeply and generalized in Tissot et al. \cite{Tissot} to the case of closed second-order indices. In the following we will refer to this method as the replication procedure.

\subsection{Towards a reliable estimation}
\label{sec:2.3}
The aim of this article is to propose a sequential procedure to estimate first-order and total effect Sobol' indices.  A practical problem concerning the estimation of these indices is how large to choose the number of evaluations to ensure that Sobol' estimates are accurate enough. Asymptotical results show that Sobol' estimates are normally distributed (\cite[Proposition 2.2]{Janon}, \cite[Proposition 3.5]{Tissot}). As a consequence, errors can be estimated through confidence intervals. However, these error estimates are only guaranteed asymptotically as the number of model evaluations goes to infinity.

@@

We will assume that we have an embedded sequence of digital nets \comment{in $\cube$, base $b$ and dimension d} as described in \cite[Sec. 2-3]{HicJim},
\begin{equation}\label{embedded_digital}
\mathcal{P}_0=\{\vect{0}\}\subset\dots\subset\mathcal{P}_m=\{\vx_i\}_{i=0}^{b^m-1}\subset\dots\subset\mathcal{P}_\infty=\{\vx_i\}_{i=0}^{\infty}.
\end{equation}
\comment{The Sobol' sequence is an example of a digital net in base two satisfying \eqref{embedded_digital}, which in dimension one corresponds to: $\mathcal{P}_0=\{0\}$, $\mathcal{P}_1=\{0,0.5\}$, $\mathcal{P}_2=\{0,0.5,0.25,0.75\}$, $\mathcal{P}_3=\{0,0.5,0.25,0.75,0.125,0.625,0.375,0.875\}$,...}

\comment{For this sequence of digital nets,} each $\mathcal{P}_m$ has a group structure under the digitwise addition:
\[
\vx \oplus \vt = \left(\sum_{\ell=1}^{\infty} [(x_{j\ell} + t_{j\ell}) \bmod b] b^{-\ell} \pmod{1} \right)_{j=1}^d,
\]
where $x_{j\ell}$ and $t_{j\ell}$ are the $b$-adic decompositions of the $j^{\rm th}$ component of points $\vx$ and $\vt$, \comment{ i.e.
\[
x_{j} = \sum_{\ell=1}^{\infty} x_{j\ell}b^{-\ell},\qquad t_{j} = \sum_{\ell=1}^{\infty} t_{j\ell}b^{-\ell}.
\]
For $b=2$, the digitwise addition is equivalent to the XOR operation.

In addition, we consider the \emph{wavenumber} space of non-negative integers $\mathbb{N}_0^d$. These non-negative integers will index the frequencies in which we decompose our integrand as a Walsh series. The space $\mathbb{N}_0^d$ is also a group under the digitwise addition:
\[
\vk \oplus \vl = \left(\sum_{\ell=0}^{\infty} [(k_{j\ell} + l_{j\ell}) \bmod b] b^{\ell} \right)_{j=1}^d,
\]
where $k_{j\ell}$ and $l_{j\ell}$ are the $b$-adic decompositions of the $j^{\rm th}$ components,
\[
k_{j} = \sum_{\ell=0}^{\infty} k_{j\ell}b^{\ell},\qquad l_{j} = \sum_{\ell=0}^{\infty} l_{j\ell}b^{\ell}.
\]
}
To relate the group structure of $\mathcal{P}_m$ with the integration error, we introduce the \emph{dual net} which establishes the link between any digital net and the \emph{wavenumber} space. A dual net $\mathcal{P}_m^\perp$ is
\begin{align*}
\mathcal{P}_m^\perp=\{\vk\in\mathbb{N}_0^d:\ip{\vk}{\vx}=0,\, \text{ for all } \vx\in\mathcal{P}_m\}, \\
\ip{\vk}{\vx} = \left(\sum_{j=1}^{d} \sum_{\ell=0}^{\infty} k_{j\ell}x_{j,\ell+1}  \pmod b \right)/b,
\end{align*}
and inherits the inverted embedded structure \eqref{embedded_digital},
\begin{equation}\label{dual_net_structure}
\mathcal{P}_0^\perp=\mathbb{N}_0^d\supset\dots\supset\mathcal{P}_\infty^\perp=\{\vect{0}\}.
\end{equation}

As shown in \cite[Sec. 3]{HicJim}, the group structure of digital nets guarantees the property below affecting any Walsh basis function $\varphi_{\vk}(\vx)=\e^{2 \pi \sqrt{-1} \ip{\vk}{\vx}}$,
\begin{equation}\label{basis_integ_prop}
\frac{1}{b^m}\sum_{\vx\in\mathcal{P}_m}\varphi_{\vk}(\vx)=
\begin{cases}
1,\quad \vk\in\mathcal{P}_m^\perp, \\
0,\quad \vk\notin\mathcal{P}_m^\perp.
\end{cases}
\end{equation}
Therefore, using the Walsh decomposition of $f\in \mathbb{L}^2([0,1]^d)$: \[
f(\vx)=\sum_{\vk\in\naturals_0^d}\hf_{\vk}\varphi_{\vk}(\vx), \]
and defining the value of the integral,
\[ I = \int_{\cube} f(\vx)\,d\vx,\]
property \eqref{basis_integ_prop} leads to
\begin{align}
\nonumber
\absolute{I - \frac{1}{b^m}\sum_{\vx\in\mathcal{P}_m}f(\vx)} &=
\absolute{\hf_{\vzero} - \frac{1}{b^m}\sum_{\vx\in\mathcal{P}_m}\sum_{\vk\in\naturals_0^d}\hf_{\vk}\varphi_{\vk}(\vx)}, \\
\nonumber
&= \absolute{\sum_{\vk\in\mathcal{P}_m^\perp\setminus\{\vzero\}}\hf_{\vk}} \\
& \leq \sum_{\vk\in\mathcal{P}_m^\perp\setminus\{\vzero\}}\absolute{\hf_{\vk}}. \label{3.1.err_bound}
\end{align}
Based on the size of $\absolute{\hf_{\vk}}$ and the structure of dual nets \eqref{dual_net_structure}, in \cite[Sec. 4.1]{HicJim} we proposed an ordering of the \emph{wavenumbers} $\tilde{\vk}(\cdot):\naturals_0\rightarrow\naturals_0^d$. \comment{This ordering $\tilde{\vk}$ is a one-to-one and onto mapping between $\naturals_0$ and $\naturals_0^d$. Thus, we can identify each $\vk\in\naturals_0^d$ with one $\kappa\in\naturals_0$ such that $\tilde{\vk}(\kappa)=\vk$. The ordering is not unique and one should choose it such that large values of $\kappa$ are mapped to smaller values of $\absolute{\hf_{\tilde{\vk}(\kappa)}}$. It also ensures that $\mathcal{P}_m^\perp\setminus\{\vzero\}=\{\tilde{\vk}(\lambda b^m)\}_{\lambda=1}^\infty$. If we identify $\hf_{\kappa}=\hf_{\tilde{\vk}(\kappa)}$, the error bound \eqref{3.1.err_bound} becomes,}
\begin{equation}\label{mapped_error_bound}
\absolute{I - \frac{1}{b^m}\sum_{\vx\in\mathcal{P}_m}f(\vx)} \le \sum_{\lambda=1}^{\infty} \left \lvert \hf_{\lambda b^m}\right \rvert.
\end{equation}
\comment{The use of the error bound \eqref{mapped_error_bound} to design and automatic algorithm requires the knowledge of the Walsh coefficients. To avoid this assumption, we will estimate them via the fast transform obtained using the precomputed function values already used to estimate the mean. We will refer to the discrete coefficients as $\tf_{m,\kappa}$,}
\[
\tf_{m,\kappa}=\tf_{m,\tilde{\vk}(\kappa)}=\frac{1}{b^m}\sum_{\vx\in\mathcal{P}_m}f(\vx)\overline{\varphi_{\tilde{\vk}(\kappa)}(\vx)}.
\]
\comment{As shown in \cite[Sec. 3]{HicJim}, the error of estimating the true coefficients using the discrete coefficients can be measured,
\begin{equation}\label{discrite_true_relationship}
\tf_{m,\kappa} = \hf_\kappa + \sum_{\lambda=1}^{\infty} \hf_{\kappa + \lambda b^m}, \qquad \text{ for all } \kappa\in\naturals_0,
\end{equation}
However, since there are at most $b^m$ distinct values of $\tf_{m,\kappa}$, we require some assumptions on the decay rate of $\hf_{\kappa}$ to transform \eqref{mapped_error_bound} into a new error bound in terms of the discrete coefficients.}

>>>>

\begin{abstract}
In the field of sensitivity analysis, Sobol' indices are sensitivity measures widely used to assess the importance of inputs of a model to its output. The estimation of these indices is often performed through Monte Carlo or quasi-Monte Carlo methods. A notable method is the replication procedure that estimates first-order indices at a reduced cost in terms of number of model evaluations.

@@

A practical problem concerning the use of these methods is how to quantify the number of model evaluations required to ensure that Sobol' estimates are accurate enough. This article addresses this challenge by proposing a reliable error bound for Sobol' indices based on digital sequences. One reason to use digital sequences is that the numerical integration convergence rates \comment{can be} $\mathcal{O}(n^{-1+\delta})$ ($n$ being the number of function values) instead of the usual $\mathcal{O}(n^{-1/2})$ for iid Monte Carlo methods. In addition, the error bound in this article is defined in terms of the discrete Walsh coefficients of the integrands involved in the Sobol' indices definition. We propose a sequential estimation procedure of Sobol' indices using the error bound as our stopping criterion. The procedure operates under the assumption that all integrands lie inside a particular cone of functions (see \cite{HicJim}).

@@

\subsection{Definition of Sobol' indices}
\label{sec:2.1}
%We adopt the same notations introduced by Owen in \cite{Owen}. 
Denote by $\vx=(x_1,\dots,x_d)$ the vector of inputs of $f$. We assume that $f$ is in some subset of $\mathbb{L}^2(\cube)$ for which $f(\vx)$ is defined for all $\vx\in\cube$, and $\mathcal{D}=\{1,\dots,d\}$ the set of dimension indexes. %The uncertainty on $\vx$ is modeled by a random vector that we suppose uniformly distributed on $\cube$.
Let $u$ be a subset of $\mathcal{D}$, $-u$ its complement and $|u|$ its cardinality. Then, $\vx_u$ represents a point in $[0,1]^{|u|}$ with components $x_j, j \in u$. Given two points $\vx$ and $\vx'$, the hybrid point $\vw=(\vx_u:{\vx'}_{-u})$ is defined as $w_j=x_j$ if $j \in u$ and $w_j=x'_j$ if $j \notin u$.% and denote by $\mu$ and $\sigma^2$ the mean $\int_{\cube}f(\vx)d{\vx}$ and variance $\int_{\cube}(f(\vx)-\mu)^2d{\vx}$ of $f$.

@@

\subsection{Estimation of Sobol' indices}
\label{sec:2.2}
In this section we review two Monte Carlo procedures for the estimation of Sobol' indices. A design is a point set $\mathcal{P}=\{\vx_i\}_{i=0}^{n-1}$ where each point is obtained by sampling each variable $x_j$ $n$ times. Each row of the design is a point $\vx_i$ in $[0,1]^d$ and each column of the design refers to samples of a variable $x_j$. Consider $\mathcal{P}=\{\vx_i\}_{i=0}^{n-1}$ and $\mathcal{P'}=\{{\vx'}_i\}_{i=0}^{n-1}$ two designs where $(\vx_i,{\vx'}_i) \iid \mathcal{U}([0,1]^{2d})$. One way to estimate the two quantities (\ref{first.order}) and (\ref{total.effect}) is via:
\begin{align}
\label{first.order.est}
\widehat{\underline{\tau}_u^2} &= \frac{1}{n} \sum \limits_{i=0}^{n-1} \left(f(\vx_{i,u}:{\vx'}_{i,-u})-f(\vx'_i)\right)f(\vx_i),\\
\label{total.effect.est}
\widehat{\ov{$\tau$}_u^2} &= \frac{1}{2n} \sum \limits_{i=0}^{n-1} (f({\vx'}_i) - f(\vx_{i,u}:{\vx'}_{i,-u}))^2, \qquad u \in \mathcal{D},
\end{align}
using for $\sigma^2$:
\comment{\begin{equation}
 \widehat{\sigma}^2 = \frac{1}{2(n-1)} \sum \limits_{i=0}^{n-1} \left[\left( f(\vx_i) - \widehat{\mu}\right)^2 + \left( f(\vx'_i) - \widehat{\mu}\right)^2\right],
 \end{equation}
with
\begin{equation}
\widehat{\mu} =  \frac{1}{2n} \sum \limits_{i=0}^{n-1} \left[ f(\vx_i)+f(\vx'_i)\right].
\label{mu.est}
\end{equation}}

Then, the Sobol' indices estimators are:
\begin{equation}
\widehat{\underline{S}}_u = \widehat{\underline{\tau}_u^2} / \widehat{\sigma}^2, \qquad
\widehat{\overline{S}}_u = \widehat{\overline{\tau}_u^2} / \widehat{\sigma}^2.
\label{common.sobol.est}
\end{equation}
Using this method, the estimation of a single pair ($\widehat{\underline{S}}_u$, $\widehat{\overline{S}}_u$) requires $3n$ evaluations of the model $f$. Thus, for all first order and total effect indices, one would need $3nd$ model evaluations. Using a combinatorial formalism, in \cite{Saltelli} Saltelli proposes the following estimation strategy:
\begin{theorem}
\label{saltelli.theorem}
The $d+2$ designs $\{\vx_{i,u}:{\vx'}_{i,-u}\}_{i=0}^{n-1}$ constructed for $u \in \{\varnothing,\{1\},\dots,$ $\{d\},\mathcal{D}\}$ allow to estimate all first-order and total effect Sobol' indices at a cost of $n(d+2)$ evaluations of the model.
\end{theorem}
The main idea of the theorem is that there is no need to reevaluate $f({\vx}_i)$ and $f({\vx'}_i)$ for each $u$. Hence, we can simply evaluate $f({\vx}_i)$ $n$ times, $f({\vx'}_i)$ $n$ times, and $f(\vx_{i,u}:{\vx'}_{i,-u})$ $nd$ times, which accounts for the $n(d+2)$ evaluations.

The $d+2$ designs of Theorem \ref{saltelli.theorem} are obtained by substituting columns of $\mathcal{P}$ for columns of $\mathcal{P}'$ according to $u$. While elegant, this approach requires a number of model evaluations that grows linearly with respect to the input \break space dimension.

A more efficient alternative to evaluate all first-order indices was proposed in \cite{Mara} and only requires $2n$ model evaluations. This alternative relies on the construction of two replicated designs. The notion of replicated designs was first introduced by McKay through his replicated Latin Hypercubes in \cite{McKay}. In order to apply this definition to other types of points, \comment{we use the generalization from \cite{GJAHMP}.}

\begin{definition}
\label{rep.designs}
Let $\mathcal{P}=\{\vx_i\}_{i=0}^{n-1}$ and $\mathcal{P}'=\{{\vx'}_i\}_{i=0}^{n-1}$ be two point sets in $[0,1]^{d}$. In these sets, all points $\vx_i$ (resp. $\vx'_i$) are coordinate-wise different, i.e. for all $(i_1,i_2) \in \{0,\dots,n-1\}^2$ such that $i_1 \neq i_2$: $$x_{i_1,j} \neq x_{i_2,j}, \qquad \text{for any  } j=1,\dots,d .$$
Let $\mathcal{P}^u=\{\vx_{i,u}\}_{i=0}^{n-1}$ (resp. ${\mathcal{P}'}^u$), $u \subsetneq \mathcal{D}$, denote the subset of dimensions of $\mathcal{P}$ (resp. $\mathcal{P}'$) indexed by $u$. We say that $\mathcal{P}$ and $\mathcal{P}'$ are two replicated designs of order $a \in \{1,\dots,d-1\}$ if for any $u \subsetneq \mathcal{D}$ such that $|u|=a$, $\mathcal{P}^u$ and ${\mathcal{P}'}^u$ are the same point set in $[0,1]^a$. We define by $\pi_u$ the permutation that rearranges the rows of ${\mathcal{P}'}^u$ into $\mathcal{P}^u$ and exclude the trivial case $\vx_i = \vx'_i$ for all $i\in\{0,\dots,n-1\}$.
\end{definition}

@@

More precisely, let $\mathcal{P}=\{\vx_i\}_{i=0}^{n-1}$ and $\mathcal{P}'=\{{\vx'}_i\}_{i=0}^{n-1}$ be two replicated designs of order $1$. Denote by $\{y_i\}_{i=0}^{n-1}=$\\$\{f(\vx_i)\}_{i=0}^{n-1}$ and $\{y'_i\}_{i=0}^{n-1}=\{f({\vx'}_i)\}_{i=0}^{n-1}$ the two sets of model evaluations obtained with $\mathcal{P}$ and $\mathcal{P}'$. From Definition \ref{rep.designs}, we know that ${\vx'}_{\pi_u(i),u}={\vx}_{i,u}$. Then,
\begin{align*}
y'_{\pi_u(i)}&= f(\vx'_{\pi_u(i),u}:{\vx'}_{\pi_u(i),-u}) \\
&= f(\vx_{i,u}:{\vx'}_{\pi_u(i),-u}).
\end{align*}
Hence, each $\underline{\tau}^2_u$ can be estimated via formula (\ref{first.order.est}) by using $y'_{\pi_u(i)}$ instead of $f(\vx_{i,u}:{\vx'}_{i,-u})$ without requiring further model evaluations for each $u$. This estimation method has been studied deeply and generalized in \comment{Tissot and Prieur} \cite{Tissot} to the case of closed second-order indices. In the following we will refer to this method as the replication procedure.

\subsection{Towards a reliable estimation}
\label{sec:2.3}
The aim of this article is to propose a sequential procedure to estimate first-order and total effect Sobol' indices.  A practical problem concerning the estimation of these indices is how large to choose the number of evaluations to ensure that Sobol' estimates are accurate enough. \comment{Asymptotic} results show that Sobol' estimates are normally distributed (\cite[Proposition 2.2]{Janon}, \cite[Proposition 3.5]{Tissot}). As a consequence, errors can be estimated through confidence intervals. However, these error estimates are only guaranteed asymptotically as the number of model evaluations goes to infinity.

@@

We will assume that we have an embedded sequence of digital nets in $\cube$, base $b$ and dimension \comment{$d$} as described in \cite[Sec. 2-3]{HicJim},
\begin{equation}\label{embedded_digital}
\mathcal{P}_0=\{\vect{0}\}\subset\dots\subset\mathcal{P}_m=\{\vx_i\}_{i=0}^{b^m-1}\subset\dots\subset\mathcal{P}_\infty=\{\vx_i\}_{i=0}^{\infty}.
\end{equation}
The Sobol' sequence is an example of a digital net in base two satisfying \eqref{embedded_digital}, which in dimension one corresponds to: $\mathcal{P}_0=\{0\}$, $\mathcal{P}_1=\{0,0.5\}$, $\mathcal{P}_2=\{0,0.5,0.25,0.75\}$, $\mathcal{P}_3=\{0,0.5,0.25,0.75,0.125,0.625,0.375,0.875\}$,...

For this sequence of digital nets, each $\mathcal{P}_m$ has a group structure under the digitwise addition:
\[
\vx \oplus \vt = \left(\sum_{\ell=1}^{\infty} [(x_{j\ell} + t_{j\ell}) \bmod b] b^{-\ell} \pmod{1} \right)_{j=1}^d,
\]
where $x_{j\ell}$ and $t_{j\ell}$ are the $b$-adic decompositions of the $j^{\rm th}$ component of points $\vx$ and $\vt$, i.e.
\[
x_{j} = \sum_{\ell=1}^{\infty} x_{j\ell}b^{-\ell},\qquad t_{j} = \sum_{\ell=1}^{\infty} t_{j\ell}b^{-\ell}.
\]
For $b=2$, the digitwise addition is equivalent to the XOR operation.

In addition, we consider the \emph{wavenumber} space of non-negative integers $\mathbb{N}_0^d$. These non-negative integers will index the frequencies in which we decompose our integrand as a Walsh series. The space $\mathbb{N}_0^d$ is also a group under the digitwise addition:
\[
\vk \oplus \vl = \left(\sum_{\ell=0}^{\infty} [(k_{j\ell} + l_{j\ell}) \bmod b] b^{\ell} \right)_{j=1}^d,
\]
where $k_{j\ell}$ and $l_{j\ell}$ are the $b$-adic decompositions of the $j^{\rm th}$ components,
\[
k_{j} = \sum_{\ell=0}^{\infty} k_{j\ell}b^{\ell},\qquad l_{j} = \sum_{\ell=0}^{\infty} l_{j\ell}b^{\ell}.
\]

To relate the group structure of $\mathcal{P}_m$ with the integration error, we introduce the \emph{dual net} which establishes the link between any digital net and the \emph{wavenumber} space. A dual net $\mathcal{P}_m^\perp$ is
\begin{align*}
\mathcal{P}_m^\perp=\{\vk\in\mathbb{N}_0^d:\ip{\vk}{\vx}=0,\, \text{ for all } \vx\in\mathcal{P}_m\}, \\
\ip{\vk}{\vx} = \left(\sum_{j=1}^{d} \sum_{\ell=0}^{\infty} k_{j\ell}x_{j,\ell+1}  \pmod b \right)/b,
\end{align*}
and inherits the inverted embedded structure \eqref{embedded_digital},
\begin{equation}\label{dual_net_structure}
\mathcal{P}_0^\perp=\mathbb{N}_0^d\supset\dots\supset\mathcal{P}_\infty^\perp=\{\vect{0}\}.
\end{equation}

As shown in \cite[Sec. 3]{HicJim}, the group structure of digital nets guarantees the property below affecting any Walsh basis function $\varphi_{\vk}(\vx)=\e^{2 \pi \sqrt{-1} \ip{\vk}{\vx}}$,
\begin{equation}\label{basis_integ_prop}
\frac{1}{b^m}\sum_{\vx\in\mathcal{P}_m}\varphi_{\vk}(\vx)=
\begin{cases}
1,\quad \vk\in\mathcal{P}_m^\perp, \\
0,\quad \vk\notin\mathcal{P}_m^\perp.
\end{cases}
\end{equation}
Therefore, using the Walsh decomposition of $f\in \mathbb{L}^2([0,1]^d)$: \[
f(\vx)=\sum_{\vk\in\naturals_0^d}\hf_{\vk}\varphi_{\vk}(\vx), \]
and defining the value of the integral,
\[ I = \int_{\cube} f(\vx)\,d\vx,\]
property \eqref{basis_integ_prop} leads to
\begin{align}
\nonumber
\absolute{I - \frac{1}{b^m}\sum_{\vx\in\mathcal{P}_m}f(\vx)} &=
\absolute{\hf_{\vzero} - \frac{1}{b^m}\sum_{\vx\in\mathcal{P}_m}\sum_{\vk\in\naturals_0^d}\hf_{\vk}\varphi_{\vk}(\vx)}, \\
\nonumber
&= \absolute{\sum_{\vk\in\mathcal{P}_m^\perp\setminus\{\vzero\}}\hf_{\vk}} \\
& \leq \sum_{\vk\in\mathcal{P}_m^\perp\setminus\{\vzero\}}\absolute{\hf_{\vk}}. \label{3.1.err_bound}
\end{align}
Based on the size of $\absolute{\hf_{\vk}}$ and the structure of dual nets \eqref{dual_net_structure}, in \cite[Sec. 4.1]{HicJim} we proposed an ordering of the \emph{wavenumbers} $\tilde{\vk}(\cdot):\naturals_0\rightarrow\naturals_0^d$. This ordering $\tilde{\vk}$ is a one-to-one and onto mapping between $\naturals_0$ and $\naturals_0^d$. Thus, we can identify each $\vk\in\naturals_0^d$ with one $\kappa\in\naturals_0$ such that $\tilde{\vk}(\kappa)=\vk$. The ordering is not unique and one should choose it such that large values of $\kappa$ are mapped to smaller values of $\absolute{\hf_{\tilde{\vk}(\kappa)}}$. It also ensures that $\mathcal{P}_m^\perp\setminus\{\vzero\}=\{\tilde{\vk}(\lambda b^m)\}_{\lambda=1}^\infty$. If we identify $\hf_{\kappa}=\hf_{\tilde{\vk}(\kappa)}$, the error bound \eqref{3.1.err_bound} becomes,
\begin{equation}\label{mapped_error_bound}
\absolute{I - \frac{1}{b^m}\sum_{\vx\in\mathcal{P}_m}f(\vx)} \le \sum_{\lambda=1}^{\infty} \left \lvert \hf_{\lambda b^m}\right \rvert.
\end{equation}
The use of the error bound \eqref{mapped_error_bound} to design \comment{an} automatic algorithm requires the knowledge of the Walsh coefficients. To avoid this assumption, we will estimate them via the fast transform obtained using the precomputed function values already used to estimate the mean. We will refer to the discrete coefficients as $\tf_{m,\kappa}$,
\[
\tf_{m,\kappa}=\tf_{m,\tilde{\vk}(\kappa)}=\frac{1}{b^m}\sum_{\vx\in\mathcal{P}_m}f(\vx)\overline{\varphi_{\tilde{\vk}(\kappa)}(\vx)}.
\]
As shown in \cite[Sec. 3]{HicJim}, the error of estimating the true coefficients using the discrete coefficients can be measured,
\begin{equation}\label{discrite_true_relationship}
\tf_{m,\kappa} = \hf_\kappa + \sum_{\lambda=1}^{\infty} \hf_{\kappa + \lambda b^m}, \qquad \text{ for all } \kappa\in\naturals_0.
\end{equation}
However, since there are at most $b^m$ distinct values of $\tf_{m,\kappa}$, we require some assumptions on the decay rate of $\hf_{\kappa}$ to transform \eqref{mapped_error_bound} into a new error bound in terms of the discrete coefficients.

For $\ell,m \in \mathbb{N}_0$ and $\ell \le m$ we introduce the following notation,
\begin{align*}
S_m(f) &=  \sum_{\kappa=\left \lfloor b^{m-1} \right \rfloor}^{b^{m}-1} \absolute{\hf_{\kappa}}, \ 
\hS_{\ell,m}(f)  = \sum_{\kappa=\left \lfloor b^{\ell-1} \right \rfloor}^{b^{\ell}-1} \sum_{\lambda=1}^{\infty} \absolute{ \hf_{\kappa+\lambda b^{m}}}, \\
\wcS_m(f)&=\hS_{0,m}(f) + \cdots + \hS_{m,m}(f)=
\sum_{\kappa=b^{m}}^{\infty} \absolute{\hf_{\kappa}},\\ 
\tS_{\ell,m}(f) &= \sum_{\kappa=\left \lfloor b^{\ell-1}\right \rfloor}^{b^{\ell}-1} \absolute{\tf_{m,\kappa}}.
\end{align*}
The sums $S_m(f)$, $\hS_{\ell,m}(f)$, $\wcS_m(f)$, and $\tS_{\ell,m}(f)$ are different from the normalized Sobol' indices $\underline{S}_u$ and $\ov{$S$}_u$. Unfortunately, the notation in articles \cite{HicJim,HicJimLi,JimHic} coincides and should not be confused with the normalized Sobol' indices notation.
